\showyourwork: a workflow for open source scientific articles

### 2021-12-21 src/ms.tex
add dir tree

\lstdefinestyle{LaTeX}{%
    language=[LaTeX]TeX,
    basicstyle=\ttfamily\footnotesize,
    texcsstyle=*\bf\color{black},
    numbers=none,
    breaklines=true,
    commentstyle=\color{red},
    frame=single,
    tabsize=2,
    keywords={begin,caption,label,end,includegraphics},   
}

@@

\section{Inferring the figure tree}

\showyourwork determines the relationship between a figure (e.g., a \texttt{*.pdf} image) and the script that generated it (e.g., a \texttt{*.py} file) via inspection of the \texttt{figure} environment in the \texttt{TeX} file. 
Specifically, it inspects the \texttt{{\textbackslash}includegraphics} and \texttt{{\textbackslash}label} commands to infer the name of the figure and the script that generated it, respectively.
Consider the following snippet, used to generate Figure~\ref{fig:eccentricity}:
%
\begin{lstlisting}[
    style=LaTeX,
    otherkeywords={figures/eccentricity.pdf,fig:eccentricity},
    emph={figures/eccentricity.pdf,fig:eccentricity},
    emphstyle={\color{blue}}
]
\begin{figure}
  \begin{centering}
    \includegraphics{figures/eccentricity.pdf}
    \caption{...}
    \label{fig:eccentricity}
  \end{centering}
\end{figure}
\end{lstlisting}

>>>>

\lstdefinestyle{bash}{%
    language=bash,
    basicstyle=\ttfamily\footnotesize,
    texcsstyle=*\bf\color{black},
    numbers=none,
    breaklines=true,
    commentstyle=\color{red},
    frame=single
}
\lstdefinestyle{LaTeX}{%
    language=[LaTeX]TeX,
    basicstyle=\ttfamily\footnotesize,
    texcsstyle=*\bf\color{black},
    numbers=none,
    breaklines=true,
    commentstyle=\color{red},
    frame=single,
    tabsize=2,
    keywords={begin,caption,label,end,includegraphics},   
}
\definecolor{lsthilite}{rgb}{0.0,0.0,1.0}

@@

\section{Repository structure}

\begin{figure}[ht!]
    \begin{centering}
        \includegraphics[width=0.5\linewidth]{figures/tree.pdf}
        \caption{
            Basic repository structure for an open source scientfic article.
        }
        \label{fig:tree}
    \end{centering}
\end{figure}

See Figure~\ref{fig:tree}.

\section{Automatic figure generation}

\showyourwork determines the relationship between a figure (e.g., a \texttt{*.pdf} image) and the script that generated it (e.g., a \texttt{*.py} file) via inspection of the \texttt{figure} environment in the \texttt{TeX} file. 
Specifically, it inspects the \texttt{{\textbackslash}includegraphics} and \texttt{{\textbackslash}label} commands to infer the name of the figure and the script that generated it, respectively.
Consider the following snippet, used to generate Figure~\ref{fig:eccentricity}:
%
\begin{lstlisting}[
    style=LaTeX,
    otherkeywords={figures/eccentricity.pdf,fig:eccentricity},
    emph={figures/eccentricity.pdf,fig:eccentricity},
    emphstyle={\color{lsthilite}}
]
\begin{figure}
  \begin{centering}
    \includegraphics{figures/eccentricity.pdf}
    \caption{...}
    \label{fig:eccentricity}
  \end{centering}
\end{figure}
\end{lstlisting}
%
The convention in \showyourwork is to infer the parent script for a figure referenced in an \texttt{includegraphics} call (in this case, {\color{lsthilite}\texttt{figures/eccentricity.pdf}}) from the figure \texttt{label}. 
Specifically, if a label starts with {\color{lsthilite}\texttt{fig:}}, the remainder of the label (e.g., {\color{lsthilite}\texttt{eccentricity}}) is interpreted as the name of a script in the \texttt{figures/} directory which can be executed to produce that figure. 
By default, figure scripts are expected to be \texttt{Python} scripts, so in this case \showyourwork will attempt to run
%
\begin{lstlisting}[
    style=bash
]
python eccentricity.py
\end{lstlisting}
%
from within the \texttt{figures/} directory to generate \texttt{eccentricity.pdf}.
